### 2017-01-18 paper/intro.tex
pass on intro

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  The relatively-recent proliferation of
multi-core machines and testing frameworks with a rich support for
parallelization enabled test suites to increase CPU usage (and execute
faster) while using existing resources available in commodity hardware
(see Section~\ref{sec:modes}).  This paper reports on an empirical
study we conducted to analyze importance of test suite parallelization
to speedup testing of open-source projects.  We argue that this a
relevant problem given the tremendous popularity of open-source
development and regression testing research.  The dimensions of
analysis in this study are as follows.

@@

%% RQ1 + RQ2
To assess how prevalent long-running test suites are in open-source
projects, we selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven}.  (Section~\ref{sec:eval}
details our selection methodology.)  To run each test suite, we used a
16GB memory Intel i7 machine\Comment{ i7-4790 Intel processor} with
eight virtual CPUs (four cores with two native threads each) and the
default Maven configuration of each project.  Our results indicate
that \percentMedLongRunning{} of the test suites take at least 1m to
run and nearly 8\% of the test suites take more than 5m to run.
Including medium and long-running test suites ($>$1m), a test suite
takes \averageMedLongRunning{} to run, on average.  These results
indicate that open-source projects often contain long running test
suites.  Furthermore, we found that although \Fix{...time
  distribution...}

>>>>

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  The proliferation of multi-core CPUs in
commodity hardware and the popularization of testing frameworks with a
rich support for parallelization (see Section~\ref{sec:modes}) enables
test suites to increase CPU usage.  This paper reports on an empirical
study we conducted to analyze importance of low-level parallelization
(\ie{}, parallel features available within each machine) to speedup
testing of open-source projects.  This is a relevant problem given the
tremendous popularity of open-source development and regression
testing research.

The dimensions of analysis in this study are as follows.

@@

%% To run each test suite, we used a
%% 16GB memory Intel i7 machine\Comment{ i7-4790 Intel processor} with
%% eight virtual CPUs (four cores with two native threads each) and the
%% default Maven configuration of each project.

%% RQ1 + RQ2
We selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven} to assess how prevalent
long-running test suites are.  Section~\ref{sec:eval} details our
methodology to select subjects and to isolate our experiments from
environmental noise.  In summary, results indicate that $\sim$21\% of
the test suites take at least 1m to run and $\sim$8\% of the test
suites take at least 5m to run.  Considering all the \numMedLong{}
projects (\percentMedLongRunning{} of
\numSubjs{})\Fix{$\leftarrow$this is not right. check macros.} in the
$>$1m group, the average execution time is \averageMedLongRunning{}.
Results also show that individual tests are typically short-running,
taking often less than half a second to run.  Furthermore, we found
that only in rare cases few test cases monopolize execution cost
associated with each test suite.  Overall, these results suggest that
test suite parallelization has the potential to optimize these test
suites.
